\papertitle

### 2017-03-09 paper/paper.tex
Improved plots, paper. Still not done ugh

\section{Introduction}
\label{sec:intro}
%Additive synthesis using a sum of sinusoids plus noise is a powerful model for
%representing audio, allowing for the easy implementation of many manipulations
%such as time-stretching and transposition. In its most basic form, peaks in the
%short-time spectrum are identified as representing sinusoids and connected based
%on some criteria. As the phase evolution of the sinusoid is assumed linear over
%the analysis frame, only the phase and frequency of the sinusoids at these
%analysis points are used to fit a plausible phase function. Recently, there has
%been interest in using higher order phase functions as the estimation of their
%parameters has been made possible by a new set of techniques of only moderate
%computational complexity using signal derivatives. Theoretically, the estimation
%of the parameters of a polynomial phase function of arbitrary order make it
%possible to approximate any analytical phase function to desired precision.
%Empirically, the use of higher order phase models allow for higher quality
%manipulations.
%
%The technique we will consider in this paper is the Distribution Derivative
%Method for its convenience: the technique does not require computing derivatives
%of the signal to be analysed. It does, however, require a
%$p$ times differentiable analysis window where $p+1$ is the order of the
%phase polynomial to be estimated.
%
%In the few reports on the technique, the window used is the Hann window. This
%window is many-times differentiable but 
%
%Complex polynomial phase models whose estimation is 
\section{The polynomial phase sinusoid}
Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
i.e., signals of the form
\begin{equation}
    \label{eq:polyphaseexp}
    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
\end{equation}
with $a_{i} \in \mathbb{C}$, have been developed. Many equivalent techniques have
been developed for estimating the $a_j$. In this paper we compare with the
Distribution Derivative Method (DDM) only, without loss of generality.

\section{The estimation of $a_j$}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions (Laurent Schwartz), the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with respect to
time variable $t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df(t)}{dt} = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) \\
    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df(t)}{dt}$ we obtain
%
\begin{multline*}
    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt \\
    = \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline*}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

@@

Although this technique can be exteded to describe a single
sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
interest to consider a signals featuring a sum of $P$ such components, i.e.,
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    s(t) = \sum_{i=1}^{P} x_{i}(t)
\end{equation}
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
In situations where multiple signal sources are known to exist (e.g., recordings
of multiple speakers or performers) such a model is plausible.

We examine how this mixture model influences the estimation of the $a_{i,j}$.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in \ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0
    \\ = 
    \sum_{i=1}^{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_i, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$.

@@

In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by
the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of
all but one component, granted the components's energy concentrations are
sufficiently separated in frequency, we desire impulse responses whose magnitude
response gives maximum
out-of-band rejection or equivalently, windows whose Fourier transform exhibits
the lowest side-lobes.

In all the publications these authors reviewed on the DDM, the window used was
the Hann window which is once-differentiable everywhere in the time-domain.
Nuttall has designed windows with lower side-lobes than the canonical Hann
window which are everywhere at least once-differentiable. It is also possible to
design approximations to aribtrary symmetrical window functions using
harmonically related cosines, as is discussed in the following section.

@@

A differentiable approximation to a symmetrical window can be designed in a
straight-forward way. (Harris) and (McGonnegal) have shown how to design optimal
windows of length $N$ samples using a linear combination of $M$ harmonically
related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

We choose the $b_{k}$ so that the window $w$'s squared approximation error to
$v$ is minimized
while having $w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{
b^{\ast}_{k} \}$ to the mathematical program
\begin{equation}
    \label{eq:searchcontwinprogram}
    \text{minimize}
    \sum_{n=0}^{N-1} ( v(n) 
        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
\end{equation}
\[
    \text{subject to} \\
    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
\]
which can be solved using constrained least-squares -- a standard numerical
linear algebra routine (Goulob and Van Loan p 585).

\section{Continuous window design example}
\label{sec:designexample}
\begin{figure*}[t]
    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_mainlobe}.eps}}
\caption{\label{fig:dpwmainlobe} Comparing the mainlobe characteristics of the
continuous 4-term Nuttall window, the digital prolate window with $W=0.008$, and
the continuous approximation to the digital prolate window.}
\end{figure*}

\begin{figure*}[t]
    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_asymptotic}.eps}}
\caption{\label{fig:dpwasymptotic} Comparing the asymptotic power spectrum
characteristics of the continuous 4-term Nuttall window, the digital prolate
window with $W=0.008$, and the continuous approximation to the digital prolate
window.}
\end{figure*}

@@

Digital prolate spheroidal windows are a parametric approximation to functions
proposed by Slepian et al. whose Fourier transform's energy is maximized in a
given bandwidth. These can be tuned to have extremely low side-lobes, at the
expense of main-lobe width.  Differentiation of these window functions may be
possible but is not as straightforward as differentiation of the sum-of-cosine
windows above. Furthermore, the windows do not generally have end-points equal to 0.
In the following we will demonstrate how to approximate a digital prolate
spheroidal window.

(Verna, Bilbao et al.) showed how to construct prolate spheroidal windows under
parameters $N$, the window length in samples, and $W$. We chose $N=512$ based on
the window length chosen in (Betser) for ease of comparison. Its parameter value
was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
at a resolution of $0.001$. The window with the closest 3db bandwidth to the
4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
shown in Fig.~\ref{fig:dpwmainlobe}~and~\ref{fig:dpwasymptotic}. We see that
this window's asymptotic roll-off is 6 dB per octave and is therefore not
continuous (Nuttall). We designed an approximate window using
Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and $N/8$ to find
the best approximation to the digital prolate window's mainlobe using a small
number of cosines. The $M$ giving the best approximation was $5$. The magnitude
response of the approximation is shown in Fig.~\ref{fig:dpwmainlobe}.  We see
that we obtain a lower highest side-lobe level by slightly sarificing the
narrowness of the mainlobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we
observe that the rolloff of the window is 18 dB per octave because it is
continuous at all points in its domain.

@@

As in (Betser) we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and compared the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, three containing the most signal energy were used in the
estimations. We see that windows with lower-sidelobes exhibit the lowest
possible error variance at the sacrifice of some estimator efficiency.

@@

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$. One of the two components was
scaled to give a desired signal power ratio with the other component. The
parameters of both components were estimated and the total squared estimation
error for all the parameters was recorded. In Fig.~\ref{fig:mixwincomp} we see
that there is generally less estimation error for components having similar
signal power. This is to be expected as the more powerful signal will mask the
other less in these scenarios. The estimation error is large when the atoms
containing the most signal energy for each component are not greatly separated
in frequency. This is likely due to the convolution of the Fourier transform of
the window with the signal -- indeed windows with a larger mainlobe exhibit a
larger `radius' in which the error of the parameter estimation will be high.
However, for atoms sufficiently separated in frequency, windows with lower
sidelobes are better at attenuating the other component and for these the
estimation error is lowest.

% TODO: Plot these windows

@@

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
%\bibliography{paper} % requires file DAFx17_tmpl.bib

>>>>

\section{Introduction}
\label{sec:intro}
Additive synthesis using a sum of sinusoids plus noise is a powerful model for
representing audio (Xerra, McAulay), allowing for the easy implementation of
many manipulations such as time-stretching and transposition (Haken-Fitz,
Marchand enhanced time-stretching).
In its most basic form, peaks in the
short-time spectrum are identified as representing sinusoids and connected based
on some criteria. As the phase evolution of the sinusoid is assumed linear over
the analysis frame, only the phase and frequency of the sinusoids at these
analysis points are used to fit a plausible phase function. Recently, there has
been interest in using higher order phase functions \cite{xuepiecewise} as the estimation of
their parameters has been made possible by a new set of techniques of only
moderate computational complexity using signal derivatives \cite{hamilton2011non}.  The use
of higher-order phase models allows for higher quality representations, for
example in the analysis of birdsong \cite{stowell2013improved} or the
regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
The original techniques estimating the parameters of higher-order phase models
considered signals containing only one component, although the technique
has been applied to mixtures of components. In addition to proposing improved
analysis techniques, the performance of the techniques on mixtures of signals is
evaluated.

%Theoretically, the estimation of the parameters of a polynomial
%phase function of arbitrary order make it possible to approximate any analytical
%phase function to desired precision.
%
%The technique we will consider in this paper is the Distribution Derivative
%Method for its convenience: the technique does not require computing derivatives
%of the signal to be analysed. It does, however, require a
%$p$ times differentiable analysis window where $p+1$ is the order of the
%phase polynomial to be estimated.
%
%In the few reports on the technique, the window used is the Hann window. This
%window is many-times differentiable but 
%
%Complex polynomial phase models whose estimation is 
\section{The polynomial phase sinusoid}
Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
i.e., signals of the form
%
\begin{equation}
    \label{eq:polyphaseexp}
    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
\end{equation}
%
with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
utilizing derivatives of the signal or the analysis window have
been developed for estimating the $a_j$. The theoretical equivalence of these
techniques is described in \cite{hamilton2011non}. This paper focuses on the
Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
analysis window and no signal derivatives, which is convenient for signal
processing applications.

In \cite{hamilton2012comparisons} the accuracy
of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
the test functions. In (Roebel) twice-differentiated windows are used to
estimate the frequency slopes of chirp signals. Results on the accuracy of
estimation for signals made of a mixture of chirps are given for the frequency
slope ($\Im{a_2}$) only, but a variety of windows are compared.

In this paper, we evaluate the performance of various once-differentiable
windows in estimating the $a_{j}$. We are interested in windows with lower
sidelobes in order to better estimate parameters of sinusoidal chirp signals in
mixture. A technique to design once-differentiable approximations to aribitrary
symmetrical windows is presented along with a design example for a
high-performance window.

\section{The estimation of $a_j$}
We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
the theory of distributions \cite{schwartz1959theorie}, the DDM
makes use of ``test
functions'' or atoms $\psi$. These atoms must be once differentiable with
respect to time variable $t$ and be non-zero only on a finite interval
$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
%
\begin{equation}
    \label{eq:ddm:inner:prod:def}
    \left\langle x , \psi \right\rangle = 
    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
\end{equation}
%
and the operator 
%
\[
\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
\]
%
Consider the weighted signal
%
\[
    f(t) = x(t) \overline{\psi}(t)
\]
%
differentiating with respect to $t$ we obtain
%
\begin{multline}
    \label{eq:ddm:weighted:sig:derivative}
    \frac{df(t)}{dt} = 
    \frac{dx}{dt}(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t) \\
    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
    + x(t)\frac{d\overline{\psi}}{dt}(t)
\end{multline}
%
Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
$\frac{df(t)}{dt}$ we obtain
%
\begin{multline*}
    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt \\
    = \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
\end{multline*}
%
or, using the operator $\mathcal{T}^{\alpha}$,
%
\[ 
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
\]
%

From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
equations
\begin{equation}
    \label{eq:ddmsyseq}
    \sum_{j=1}^{Q} j a_j 
    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
\end{equation}
for $1 \leq r \leq R$.

To estimate $a_0$ we write the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \eta (t)
\]
where $\eta (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \eta , \gamma \right\rangle
\]
The inner-product between $\eta$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

@@

Although this technique can be exteded to describe a single
sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
interest to consider signals featuring a sum of $P$ such components, i.e.,
%
\begin{equation}
    \label{eq:polyphaseexpmix}
    s(t) = \sum_{i=1}^{P} x_{i}(t)
\end{equation}
%
with
%
\[
    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
\]
%
In situations where multiple signal sources are known to exist (e.g., recordings
of multiple speakers or performers) such a model is plausible.

We examine how this mixture model influences the estimation of the $a_{i,j}$.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0
    \\ = 
    \sum_{i=1}^{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

@@

In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by
the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of
all but one component, granted the components's energy concentrations are
sufficiently separated in frequency, we desire impulse responses whose magnitude
response gives maximum
out-of-band rejection or equivalently, windows whose Fourier transform exhibits
the lowest sidelobes.

In all the publications these authors reviewed on the DDM, the window used was
the Hann window which is once-differentiable everywhere in the time-domain.
Nuttall \cite{nuttall1981some} has designed windows with lower sidelobes than the canonical Hann
window which are everywhere at least once-differentiable. It is also possible to
design approximations to aribtrary symmetrical window functions using
harmonically related cosines, as is discussed in the following section.

@@

A differentiable approximation to a symmetrical window can be designed in a
straight-forward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

We choose the $b_{k}$ so that the window $w$'s squared approximation error to
$v$ is minimized
while having $w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{
b^{\ast}_{k} \}$ to the mathematical program
\begin{equation}
    \label{eq:searchcontwinprogram}
    \text{minimize}
    \sum_{n=0}^{N-1} ( v(n) 
        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
\end{equation}
\[
    \text{subject to} \\
    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
\]
which can be solved using constrained least-squares -- a standard numerical
linear algebra routine \cite[p.~585]{golub1996matrix}.

\section{Continuous window design example}
\label{sec:designexample}
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpwmainlobe} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}

@@

Digital prolate spheroidal windows are a parametric approximation to functions
proposed by whose Fourier transform's energy is maximized in a given bandwidth
\cite{slepian1978prolate}. These can be tuned to have extremely low sidelobes,
at the expense of main-lobe width.  Differentiation of these window functions
may be possible but is not as straightforward as differentiation of the
sum-of-cosine windows above. Furthermore, the windows do not generally have
end-points equal to 0. In the following we will demonstrate how to approximate
a digital prolate spheroidal window with one that is everywhere at least
once-differentiable.

In \cite{verma1996digital} it was shown how to construct digital prolate
spheroidal windows under parameters $N$, the window length in samples, and a
parameter $W$. We chose $N=512$ based on the window length chosen in
\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
at a resolution of $0.001$. The window with the closest 3db bandwidth to the
4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
shown in Fig.~\ref{fig:dpwmainlobe}~and~\ref{fig:dpwasymptotic}. We see that
this window's asymptotic roll-off is 6 dB per octave and is therefore has a
discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
$N/8$ to find the best approximation to the digital prolate window's main lobe
using a small number of cosines. The $M$ giving the best approximation was $5$.
The magnitude response of the approximation is shown in
Fig.~\ref{fig:dpwmainlobe}.  We see that we obtain a lower highest sidelobe
level than the Nuttall and Prolate windows by slightly sarificing the narrowness
of the main lobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we observe that
the rolloff of the window is 18 dB per octave because it is once-differentiable
at all points in its domain.

@@

As in \cite{betser2009sinusoidal} we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and compared the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, the three atoms whose inner products were greatest were used in
the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
lower sidelobes exhibit the lowest possible error variance at the sacrifice of
some estimator efficiency.

@@

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$. One of the two components was
scaled to give a desired signal power ratio with the other component. The
parameters of both components were estimated and the total squared estimation
error for all the parameters was recorded. In Fig.~\ref{fig:mixwincomp} we see
that there is generally less estimation error for components having similar
signal power. This is to be expected as there will be less masking of the weaker
signal in these scenarios. The estimation error is large when the atoms
containing the most signal energy for each component are not greatly separated
in frequency. This is due to the convolution of the Fourier transform of
the window with the signal, and agrees with what was predicted by
Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit a
larger `radius' in which the error of the parameter estimation will be high.
However, for signals with local inner product maxima are with atoms sufficiently
separated in frequency, windows with lower sidelobes are better at attenuating
the other component and for these the estimation error is lowest.

@@

%\newpage
%\nocite{*}
\bibliographystyle{IEEEbib}
\bibliography{paper} % requires file DAFx17_tmpl.bib
